### 2021-06-11 rad-icfp-2021/abstract.tex
some change abstract

\begin{abstract}
    We introduce an efficient source-code transformation for reverse-mode differentiation on an expressive purely functional language that does not introduce mutation.
    We show that our transformation is correct and verifies the cheap gradient principle. 
    Our transformation is presented as a compilation scheme through a novel intermediate representation we call unary form.
    We obtain provably efficient gradients by performing general partial evaluation optimisations after our reverse-mode transformation as opposed to hand-crafted ones.
    For simple first-order programs, the obtained outputs look like static single assignment (SSA) code. 
    For arrays, our transformation preserves parallelism as much as possible. 
    Our work emphasizes modularity and our language can easily be enriched with more optimised primitives as required for some speedups in practice.
\end{abstract}

>>>>

\begin{abstract}
    Deep learning is moving towards increasingly sophisticated optimization objectives that employ
    tensors and operations on tensors.
    Reverse-mode differentiation is used for optimisation, 
    but it doesn't preserve purity of the underlying program and makes it notoriously harder to optimise.
    In a purely functional setting, most array operations can be expressed conveniently using map and fold.
    We present a differentiable programming language, that is the first to deliver en efficient pure and parallel friendly reverse-mode differentiation on
    an expressive array language. 
    We show that our transformation is semantically correct and verifies the cheap gradient principle. 
    Our transformation is presented as a compilation scheme through a novel intermediate representation we call unary form.
    We obtain provably efficient gradients by performing general partial evaluation optimisations after our reverse-mode transformation as opposed to manually derived ones.
    For simple first-order programs, the obtained output programs ressemble static single assignment (SSA) code. 
    We emphasize the modularity of our approach and show how our language can easily be enriched with more optimised primitives as required for some speedups in practice.
\end{abstract}
